Factors Influencing Early Childhood Comprehension of American English with a Bayesian Model

### 2024-12-04 paper/paper.qmd
update paper

@@

* Target Population: Infants and toddlers aged 8 to 30 months whose parents are willing to report on their child's language development.

@@

@@

Stability Across Time: Longitudinal data from CDI demonstrate high stability in early language scores. Studies like De Houwer et al. (2005) show significant correlations in CDI measurements across different ages, indicating that early language acquisition remains relatively stable over time.

@@

>>>>

## Create API for the Reduced Model

To make the reduced model more practical and usable, we created an API that provides real-time predictions of comprehension based on user-provided inputs. Researchers can input variables like a child's age, production score and caregiver's education to receive predictions with credible intervals. By using the \texttt{plumber} [@citeplumber], the API ensures usability and integration into various workflows.

@@

* Target Population: Infants and toddlers aged 8 to 36 months whose parents are willing to report on their child's language development.

@@

### Variables

* Age Groups: 8-12 months, 13-24 months, 25-36 months
* Gender: Boy, Girl
* Caregiver Education Level: Primary, Secondary, Some College, Bachelor’s, Graduate, Other
* Household Income Level: <$30,000, $30,000-$59,999, $60,000-$99,999, >$100,000
* Caregiver Employment Status: Employed, Unemployed, Student, Homemaker
* Language at Home: Monolingual, Bilingual, Multilingual
* Geographic Region: Urban, Suburban, Rural
* Race: White, Black/African American, Hispanic/Latino, Asian, Native, Other

@@

Stability Across Time: Longitudinal data from CDI demonstrate high stability in early language scores. Studies like De Houwer [@HOUWER2005], showing major correlations in CDI measurements across different ages, indicating that early language acquisition remains relatively stable over time.

@@

## Survey implementation and Structure
To reach a diverse audience of caregivers, multiple distribution channels will be used. The link to the survey will be distributed via email invitations, community events, and targeted social media advertisements. The link to the survey is [here](https://forms.gle/2qVDdWk764dy16Jc6).

### Budget Allocation

* Survey Panel Recruitment: $20,000
* Community Outreach: $10,000
* Incentives (Gift Cards and Lotteries): $10,000
* Data Cleaning and Validation: $5,000
* Advertising on Social Media: $5,000

### Survey structure

**Survey introduction:**

Welcome!

We are conducting a survey to better understand the language development of children aged 8 to 36 months. Your participation is crucial in helping us gain valuable insights into early language acquisition and the factors that influence it.

Please note:

* All responses are confidential and will be used for research purposes only.
* This survey will take approximately 10 minutes to complete.
* Your participation is entirely voluntary, and you may withdraw at any time.
* All questions marked with an asterisk (*) are required.
* There are no right or wrong answers, we appreciate your honest opinions.

If you have any questions or concerns, please feel free to contact our research team at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com) (Ziyuan Shen).

As a thank you for your participation, you will be entered into a raffle to win a grand prize of a gift card. We are deeply grateful for your participation and appreciate the time and effort that you put in.

**Survey question:**

**Part 1: Eligibility and Consent**

1. Is your child between the ages of 8 and 36 months?\
* Yes / No\
2. Are you the primary caregiver of the child?\
* Yes / No\
3. Are you willing to provide information about your child’s language development?\
* Yes / No

**Part 2: Demographics**

4. How old is your child?\
* 8-12 months / 13-24 months / 25-36 months\
5. What is your child's gender?\
* Boy / Girl / Prefer not to say\
6. What is your child’s race or ethnicity? (Other, please specify)\
* White / Black / African American / Hispanic or Latino / Asian / Other\
7. What is your highest level of education?(Other, please specify)\
* Primary / Secondary / Some College / Bachelor’s Degree / Graduate Degree / Other\
8. What is your current employment status? (Other, please specify)\
* Employed / Unemployed / Student / Homemaker/ Other\
9. What is your household income level?\
* Less than $30,000 / $30,000-$59,999 / $60,000-$99,999 / Greater than $100,000 / Prefer not to say\
10. How many language(s) do you speak at home?\
* Monolingual (One language) / Bilingual (Two languages) / Multilingual (Three or more languages)\

**Part 3: Child's Language Development**

11. At what age did your child start saying their first word?\
* 8-12 months / 13-24 months / 25-36 months\
12. How often does your child use words or phrases (like “mama”, “more”)?\
* Frequently (several times a day) / Occasionally (once or twice a day) / Rarely / Not yet\
13. Does your child use gestures (like waving, pointing) to communicate?\
* Yes, often / Occasionally / No\
14. How would you rate your child’s vocabulary comprehension?\
* Understands basic words (like names of family members) / Understands common household objects (like cup, ball) / Understands more complex phrases (like “Give me the red ball”) / Does not yet understand any words

**Part 4: Child's Language Environment**

15. How often do you engage in activities that promote language development (like reading, or singing songs)?\
* Daily / Several times a week / Once a week or less / Never\
16. Do you use any of the following methods to support your child’s language development? (Check all that apply)\
* Reading books aloud / Singing songs / Playing interactive games (like peek-a-boo) / Speaking to the child in multiple languages / None of the above\
17. How often does your child interact with other children?\
* Frequently / Occasionally / Rarely / Does not interact with other children

**Part 5: Additional Information**

18. Do you believe there are any factors that have particularly influenced your child’s language development? (Such as: socioeconomic status, exposure to multiple languages, developmental disorders)\
* Yes / No\
19. Do you have any concerns about your child’s language development?\
* Yes / No

**Part 6: Verify**

20. Please select 'Agree' to verify that you are paying attention.\
* Agree / Disagree\
21. Do you agree to participate in this survey? Your responses will be kept confidential and used only for research purposes.\
* Yes / No

**End Part**

Thank you for participating!

Your responses are valuable to our research on early language development. If you have any questions or would like more information about our research, please feel free to contact us at [winniekeai23@gmail.com](mailto:winniekeai23@gmail.com)(Ziyuan Shen).
